Exp 13 write-up

### 2023-08-31 writing/DGfS2023-abstract/write-up.tex

\subsection{The effect of the prior probability of the context on naturalness ratings}

@@

%Here, I will plot, for each of the 20 predicates (target stimuli), the mean naturalness rating in the two contexts (explicit ignorance, neutral). 
%
%Expectations:
%    - Mandelkern et al 2020: presupposition triggers (factives) have lower naturalness ratings in explicit ignorance context than neutral context than non-factives, for which no difference is expected.
%    - Degen & Tonhauser 2022: the differences between the two contexts are gradient across the 20 predicates, without a clear distinction between factive and non-factive predicates.
%
%Models (fit only to target data):
%
%A. naturalness rating ~ factivity (RL: factive) * context (RL: explIgnorance), by-item (combination of predicate and CC) and by-participant intercepts, factivity slope for participant, and context slopes for item and participant
%
%Expectations based on Mandelkern et al 2020:
%- significant main effect of factivity, positive coefficient: nonfactive predicates better in explIgnorance context than factive ones
%- significant main effect of context, positive coefficient: factive predicates better in neutral context than explIgnorance 
%- interaction: positive coefficient: higher naturalness ratings for nonfactive predicates in neutral context than factive ones in explIgnorance context
%
%?%B. naturalness ~  expression (RL: predicate with smallest naturalness difference between the two contexts) * context (RL: explIgnorance), by-item and by-participant intercepts, and context slopes for item and participant. 
%
%Idea in choosing RL: when there is no difference, this is not a presupposition trigger.
%
%Expectations based on Degen & Tonhauser 2022:
%        - main effect of expression: 
%            - positive coefficient: naturalness ratings for the expression in explIgnorance context is higher than for RL expression (suggests projection of CC is easier to suppress)
%            - negative coefficient: naturalness ratings for the expression in neutral context is lower than for RL expression (suggests projection of CC is harder to suppress)
%        - main effect of context (will ideally be not significant at RL, to interpret interaction)
%        - interaction:
%            - positive coefficient: naturalness rating for the expression in neutral context is higher than for RL expression in explIgnorance context (uninteresting)
%            - negative coefficient: naturalness rating for the expression in neutral context is lower than for RL expression in explIgnorance context (uninteresting)
%
%Comparison of models A and B with AIC to identify whether the factivity-based model A or the predicate-based model B capture more variance in the data (see de Marneffe, Simons & Tonhauser 2019 SuB, Degen & Tonhauser 2022).
%
%Third analysis: Do the naturalness ratings in explicit ignorance contexts and the ?certain that? ratings get at the same underlying theoretical construct (namely speaker commitment)?
%
%    - Plot the mean naturalness ratings of the CCs of the 20 clause-embedding predicates against their mean certainty ratings.
%    - Calculate Spearman rank correlation.
%    - If the two measures get at the same underlying theoretical construct, then we expect to find a negative correlation between the two measures such that the higher the mean naturalness rating is (that is, the more the CC does not project), the lower the mean ?certain that? rating.
%
\section{Discussion}\label{s4}

>>>>

\subsection{The effect of the prior probability of the CC on naturalness ratings}

@@

Here the predicates are ordered by the mean certainty rating (Language paper, Exp.1a).

\begin{figure}[h!]
\centering
\includegraphics[width=.8\textwidth]{../../results/main/13explicitIgnorance/graphs/ORDER-by-LANGUAGE-naturalness-by-context-and-predicate}
\caption{Mean naturalness ratings by expression and context. Error bars indicate 95\% bootstrapped confidence intervals.}\label{fig:acc-by-context}
\end{figure}

%
%Expectations:
%    - Mandelkern et al 2020: presupposition triggers (factives) have lower naturalness ratings in explicit ignorance context than neutral context than non-factives, for which no difference is expected.
%    - Degen & Tonhauser 2022: the differences between the two contexts are gradient across the 20 predicates, without a clear distinction between factive and non-factive predicates.
%
%Models (fit only to target data):
%
%A. naturalness rating ~ factivity (RL: factive) * context (RL: explIgnorance), by-item (combination of predicate and CC) and by-participant intercepts, factivity slope for participant, and context slopes for item and participant
%
%Expectations based on Mandelkern et al 2020:
%- significant main effect of factivity, positive coefficient: nonfactive predicates better in explIgnorance context than factive ones
%- significant main effect of context, positive coefficient: factive predicates better in neutral context than explIgnorance 
%- interaction: positive coefficient: higher naturalness ratings for nonfactive predicates in neutral context than factive ones in explIgnorance context
%
%?%B. naturalness ~  expression (RL: predicate with smallest naturalness difference between the two contexts) * context (RL: explIgnorance), by-item and by-participant intercepts, and context slopes for item and participant. 
%
%Idea in choosing RL: when there is no difference, this is not a presupposition trigger.
%
%Expectations based on Degen & Tonhauser 2022:
%        - main effect of expression: 
%            - positive coefficient: naturalness ratings for the expression in explIgnorance context is higher than for RL expression (suggests projection of CC is easier to suppress)
%            - negative coefficient: naturalness ratings for the expression in neutral context is lower than for RL expression (suggests projection of CC is harder to suppress)
%        - main effect of context (will ideally be not significant at RL, to interpret interaction)
%        - interaction:
%            - positive coefficient: naturalness rating for the expression in neutral context is higher than for RL expression in explIgnorance context (uninteresting)
%            - negative coefficient: naturalness rating for the expression in neutral context is lower than for RL expression in explIgnorance context (uninteresting)
%
%Comparison of models A and B with AIC to identify whether the factivity-based model A or the predicate-based model B capture more variance in the data (see de Marneffe, Simons & Tonhauser 2019 SuB, Degen & Tonhauser 2022).
%

\subsection{Measuring speaker belief in the CC}

Do the naturalness ratings in explicit ignorance contexts and the inference ratings get at the same underlying theoretical construct, namely speaker belief in the CC?

Spearman rank correlation: -.62

\begin{figure}[h!]
\centering
\includegraphics[width=.7\textwidth]{../../results/main/13explicitIgnorance/graphs/mean-acceptability-against-mean-certainty}
\caption{Mean naturalness ratings by mean certainty ratings. Error bars indicate 95\% bootstrapped confidence intervals.}\label{fig:acc-by-certain}
\end{figure}

%
%    - Plot the mean naturalness ratings of the CCs of the 20 clause-embedding predicates against their mean certainty ratings.
%    - Calculate Spearman rank correlation.
%    - If the two measures get at the same underlying theoretical construct, then we expect to find a negative correlation between the two measures such that the higher the mean naturalness rating is (that is, the more the CC does not project), the lower the mean ?certain that? rating.
%
\section{Discussion}\label{s4}
